AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
paper inteiro basicamente pronto pra send. falta todos e detalhes menores.

The AA methodology is not restricted to software development, even though it was
built for the latter. As of this
writing there is an entertainment studio, Pula Pirata~\footnote{
\url{www.pulapirata.com}}, that has started to use AA to manage their creative activities.
Other people with no software background, like social scientists, musicians and
activists also have been using AA and contributing for its improvement.

@@

There are many aspects of the work which remain unfinished. Other client
interfaces to report micrologs -- the `Twitter-like' messages -- from different
interfaces beyond IRC, \eg, internet social services and email, can make the use of
AA easy and widespread, turning AA an ubiquitous system, presented on everyday
communication channels. Even the actual work logs generated by the Lab Macambira
and Pula Pirata collectives since July of 2011 could be
vastly statistically analyzed aiming to recognize patterns in the behavior of
individuals and their productions.

\section*{Acknowledgments}
%The authors would like to thank NSF and CNPq.

We would like to also thank AA: the present research and even this
manuscript was written using AA. The complete log is on-line at
\url{www.pulapirata.com/skills/aa}.

>>>>

The AA methodology is not restricted to software development, even though it was
designed for the latter. As of this
writing there is an entertainment studio, Pula Pirata~\footnote{
\url{www.pulapirata.com}}, that has started to use AA to manage their creative activities.
Other people with no software background, like social scientists, musicians and
activists also have been using AA and contributing for its improvement.

@@

There are many aspects of the work which remain unfinished. Additional
ubiquitous client
interfaces for micrologging -- the `Twitter-like' messages -- from different
interfaces beyond IRC, \eg, web social services and email, would greatly make the use of
AA easier and more widespread, turning AA a truly ubiquitous and replicable system, presented on everyday
communication channels. Another research direction is that the actual work logs
generated by the Lab Macambira and Pula Pirata collectives since July of 2011
could be vastly statistically analyzed aiming to recognize patterns in the
behavior of individuals and their creative production process.

\section*{Acknowledgments}
%TODO The authors would like to thank NSF and CNPq.

We would like to thank AA: the present research and even this
manuscript was written using AA. The complete log is on-line at
\url{www.pulapirata.com/skills/aa}.
